Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2

### 2023-01-31 Paper/paper.tex
battery charge calculation added

The battery behavior monitors the robot's battery and decides if the robot should navigate to a new goal location. The decision is based on the current battery charge and the estimated energy consumption to reach the new goal. The energy expenditure was predicted using a linear function and considering the idle consumption and energy to drive the motors. A safety factor was added to the energy estimation function to consider scenarios where the robot may need to reroute or stop. A battery package was created for simulation purposes and updates the battery charge every second. The battery package subscribes to the command velocity topic and decreases the battery charge for every message received. The consumption rates are not close to reality but were chosen for rapid testing.

@@

The ROSBot 2.0 by Husarion has been selected as the test platform for real world scenarios. It is a four-wheeled robot equipped with a suite of sensors, including LiDAR, IMU, wheel encoders and range sensors. To advance the ROSBot to a higher level of autonomy the proposed system architecture has been implemented. The battery charge module and the collision detection module were required to be adapated from the simulation to function on the real robot. The collision detection module is based on the IMU data instead of a simulated bumper sensor. The battery module estimates the remaining charge by taking the battery voltage, the power consumption of every component and the movement of the robot into account thus assuring that the robot has enough charge left to navigate to a goal.

% The ROSBot robot requires several crucial modules to be developed for successful real-world experiments. One such module is the battery monitoring module, which is responsible for monitoring the battery level and providing updates to the rest of the system. This is crucial as it ensures the robot operates safely within its battery capacity and prevents unexpected power-off during operation. Another important module is the collision detection module, which helps the robot detect obstacles in its environment and respond accordingly. This module is essential for the robot's safety as it prevents damage to itself or other actors in the environment. The development of these modules is essential for ensuring the ROSBot's robustness and safe operation in real-world scenarios.

>>>>

The battery behavior monitors the robot's battery and decides if the robot should navigate to a new goal location. The decision is based on the current battery charge and the estimated energy consumption to reach the new goal. The energy expenditure was predicted using a linear function and considering the idle consumption and energy to drive the motors. A safety factor was added to the energy estimation function to consider scenarios where the robot may need to stop navigation.. A battery package was created for simulation purposes and updates the battery charge every second. The battery package subscribes to the command velocity topic and decreases the battery charge for every message received. The consumption rates are not close to reality but were chosen for rapid testing.

@@

The ROSBot 2.0 by Husarion has been selected as the test platform for real world scenarios. It is a four-wheeled robot equipped with a suite of sensors, including LiDAR, IMU, wheel encoders and range sensors. To advance the ROSBot to a higher level of autonomy the proposed system architecture has been implemented. The battery charge module and the collision detection module were required to be adapated from the simulation to function on the real robot. The collision detection module is based on the IMU data instead of a simulated bumper sensor.

The battery module estimates the remaining charge by taking the battery voltage, the power consumption of every component and the movement of the robot into account thus assuring that the robot has enough charge left to navigate to a given goal. Following function is used to determine the current state of charge of the battery: \[Batt_{SoC}(t) = Batt_{SoC}(t-1)-\frac{\frac{P_{components}}{V_{measured}}}{Batt_{capacity}}* t_{timestep} *100\] where $Batt_{SoC}$ is the charge in percentage, $t$ is the time of calculation in hours, $t_{timestep}$ the time step in seconds and $P_{components}$ the combined power consumption of every component connected to the robot in Watt. $P_{components}$ changes depending on the speed of the robot. The calculation assumes a fully charged battery.
